### 2020-08-28 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-10 13:51:28
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
	(203.52,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,490.17) --
	(  0.00,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
	(232.04,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,518.69) --
	(  0.00,232.04);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
	(260.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,547.21) --
	(  0.00,260.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,416.78) --
	(103.65,416.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.64,409.37) --
	( 99.64,422.22);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.64,413.56) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.25,476.46) --
	(190.95,476.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.73,475.74) --
	(188.73,477.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,472.43) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.21,474.21) --
	(104.27,474.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.34,473.61) --
	(102.34,474.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.34,470.18) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,416.10) --
	(103.73,416.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.87,410.35) --
	( 99.87,420.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.87,412.07) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.40,387.89) --
	(115.90,387.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65,384.62) --
	(106.65,390.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.65,384.99) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,483.66) --
	(195.01,483.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.29,483.25) --
	(194.29,484.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.29,480.76) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.24,453.03) --
	(151.45,453.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.58,451.65) --
	(148.58,454.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.58,449.80) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,479.26) --
	(197.83,479.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.99,477.50) --
	(196.99,480.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.99,475.23) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.36,483.73) --
	(188.58,483.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.98,483.50) --
	(187.98,483.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.98,479.70) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.83,449.81) --
	(142.53,449.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.76,448.18) --
	(140.76,451.31);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.76,445.77) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.30,448.54) --
	(152.66,448.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.31,447.26) --
	(149.31,449.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.31,445.63) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,488.02) --
	(199.40,488.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,487.58) --
	(199.00,488.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,485.12) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.84,422.09) --
	(126.52,422.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.64,409.09) --
	(122.64,429.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.64,418.86) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.62,458.97) --
	(195.24,458.97);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.51,454.93) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,477.15) --
	(163.23,477.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.95,476.14) --
	(162.95,478.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.95,473.11) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.91,421.56) --
	(120.70,421.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.17,406.76) --
	(117.17,430.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.17,417.53) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.20,409.98) --
	(134.18,409.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.79,405.95) --
	(129.79,413.35);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.79,407.07) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.21,485.10) --
	(197.03,485.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.62,484.28) --
	(196.62,485.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,482.19) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.77,432.05) --
	(140.26,432.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.68,429.18) --
	(135.68,434.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.68,428.82) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.99,483.34) --
	(200.70,483.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.86,480.63) --
	(199.86,485.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,479.30) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.36,482.25) --
	(177.58,482.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.47,482.07) --
	(177.47,482.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,478.22) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.12,451.72) --
	(147.88,451.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.79,449.82) --
	(141.79,453.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.79,447.69) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.74,437.84) --
	(147.60,437.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.88,434.82) --
	(142.88,440.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.88,434.94) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,487.58) --
	(198.98,487.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.14,487.05) --
	(198.14,488.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.14,484.68) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,460.68) --
	(181.15,460.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.37,456.94) --
	(179.37,463.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.37,457.45) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.94,486.46) --
	(184.37,486.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.33,482.75) --
	(176.33,489.60);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.33,482.42) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.15,482.18) --
	(197.23,482.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.69,481.57) --
	(196.69,482.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.69,478.15) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.45,441.52) --
	(161.00,441.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.57,436.94) --
	(157.57,445.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,437.48) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.01,463.73) --
	(184.30,463.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.82,459.32) --
	(181.82,467.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,460.82) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.90,498.16) --
	(211.56,498.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.27,495.77) --
	(210.27,500.30);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.27,495.25) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.64,472.51) --
	(197.79,472.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.95,470.68) --
	(194.95,474.19);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.95,469.28) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.60,491.62) --
	(178.99,491.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.91,490.07) --
	(176.91,493.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.91,487.58) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.25,482.68) --
	(197.61,482.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.43,482.27) --
	(197.43,483.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.43,478.65) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.17,459.25) --
	(178.40,459.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.85,457.81) --
	(176.85,460.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.85,455.21) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.79,467.29) --
	(192.74,467.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,464.24) --
	(185.37,469.95);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,464.39) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,501.36) --
	(212.84,501.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.78,500.78) --
	(212.78,501.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.78,498.46) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:15
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/$10^6$ states [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/$10^6$ states [cons (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,403.16) --
	(175.00,578.16);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (302.44,578.16) --
	(302.44,477.44) --
	(  0.00,175.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00,365.13) --
	(213.03,578.16);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (302.44,578.16) --
	(302.44,515.47) --
	(  0.00,213.03);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00,327.11) --
	(251.05,578.16);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (302.44,578.16) --
	(302.44,553.49) --
	(  0.00,251.05);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,464.39) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.36) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,388.34) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 70.80,423.36) --
	( 93.23,423.36);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.25,418.92) --
	( 84.25,427.19);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 84.25,420.14) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.42,463.51) --
	(187.31,463.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.24,460.11) --
	(174.24,466.53);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.24,459.48) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 73.08,470.98) --
	( 83.11,470.98);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.55,469.19) --
	( 78.55,472.65);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 78.55,466.94) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 64.94,418.41) --
	(105.90,418.41);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.45,409.17) --
	( 92.45,425.31);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 92.45,414.38) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (  0.00,383.37) --
	( 89.39,383.37);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 70.64,364.91) --
	( 70.64,394.30);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 70.64,380.46) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.11,478.20) --
	(192.04,478.20);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.62,477.22) --
	(190.62,479.15);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.62,475.30) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.31,460.60) --
	(178.05,460.60);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.71,458.59) --
	(176.71,462.48);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.71,457.38) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.70,475.32) --
	(192.51,475.32);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.14,473.33) --
	(191.14,477.17);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.14,471.28) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.74,481.34) --
	(184.36,481.34);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.05,481.07) --
	(184.05,481.61);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.05,477.31) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.07,451.67) --
	(165.83,451.67);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.01,449.52) --
	(164.01,453.66);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.01,447.64) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.90,457.02) --
	(176.90,457.02);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.44,455.90) --
	(175.44,458.10);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.44,454.12) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.63,481.06) --
	(191.86,481.06);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.26,480.49) --
	(191.26,481.62);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.26,478.16) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.76,418.47) --
	(118.07,418.47);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.09,416.16) --
	(115.09,420.60);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.09,415.24) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.82,478.07) --
	(195.49,478.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.67,476.87) --
	(194.67,479.21);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.67,474.03) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.00,483.62) --
	(190.59,483.62);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.30,483.50) --
	(190.30,483.75);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.30,479.59) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 97.72,398.46) --
	(103.70,398.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.88,395.62) --
	(100.88,401.02);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.88,394.42) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.09,427.60) --
	(144.44,427.60);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.90,423.74) --
	(141.90,430.98);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.90,424.69) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.06,483.35) --
	(195.09,483.35);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.58,483.08) --
	(194.58,483.61);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.58,480.44) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.85,441.25) --
	(135.49,441.25);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.82,438.28) --
	(132.82,443.93);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.82,438.02) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.60,478.27) --
	(196.71,478.27);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.68,477.02) --
	(195.68,479.46);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.68,474.23) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.20,480.37) --
	(183.91,480.37);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.06,479.98) --
	(183.06,480.76);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.06,476.34) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.31,439.83) --
	(129.99,439.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.85,438.03) --
	(126.85,441.53);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.85,435.80) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.31,436.72) --
	(141.06,436.72);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.46,434.86) --
	(137.46,438.47);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.46,433.82) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.13,484.10) --
	(196.02,484.10);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.09,483.74) --
	(195.09,484.46);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.09,481.20) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.42,409.91) --
	(113.41,409.91);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.30,400.41) --
	(107.30,416.95);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.30,406.68) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.90,469.29) --
	(192.29,469.29);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.73,467.51) --
	(189.73,470.97);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.73,465.26) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.49,472.05) --
	(150.55,472.05);
